Gray-Box Optimization using the Parameter-less Population Pyramid

### 2015-04-02 Gray Box Optimization using the Parameter-less Population Pyramid/main.tex
Made github link point to "release" section

For each problem class tested, we generated 50 instances.
Extreme problem sizes were chosen to stress each algorithm.
Each method was run once on each instance, and limited to 3 hours of computation and 4 GB of memory.
Runs were performed on 2.5GHz Intel Xeon E5-2670v2 processors using the C++11 code available
from our website.\footnote{\url{https://github.com/brianwgoldman/GrayBoxOptimization}}
Each time the run achieved a new best fitness we recorded the current amount of processing time used.
Timing includes the discovery of subgraphs to allow for comparison between different radius values.
When reporting the ``best'' fitness for an instance we mean the best fitness found by any method before
the time limit is reached. On all Nearest Neighbor NKq instances the ``best'' fitness
is also the global optimum, verified using dynamic programming. For Ising Spin Glass the ``best'' fitness
was the global optimum 44 out of 50 times.

>>>>

For each problem class tested, we generated 50 instances.
Extreme problem sizes were chosen to stress each algorithm.
Each method was run once on each instance, and limited to 3 hours of computation and 4 GB of memory.
Runs were performed on 2.5GHz Intel Xeon E5-2670v2 processors using the C++11 code available
from our website.\footnote{\url{https://github.com/brianwgoldman/GrayBoxOptimization/releases}}
Each time the run achieved a new best fitness we recorded the current amount of processing time used.
Timing includes the discovery of subgraphs to allow for comparison between different radius values.
When reporting the ``best'' fitness for an instance we mean the best fitness found by any method before
the time limit is reached. On all Nearest Neighbor NKq instances the ``best'' fitness
is also the global optimum, verified using dynamic programming. For Ising Spin Glass the ``best'' fitness
was the global optimum 44 out of 50 times.
